SI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''

### 2018-09-10 reports/preprint.tex
cleaning the SI a bit

\institution{${a}$~Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK. \\
${b}$~Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK. \\
${c}$~European Spallation Source, SE-211 00 Lund, Sweden. \\
${d}$~Department of Physical Chemistry, Lund University, SE-211 00 Lund, Sweden. \\
${e}$~Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble, France. \\
${f}$~Division of Pharmacy and Optometry, University of Manchester, Manchester, \\
\indent M13 9PT, UK. \\
${g}$~ISIS Neutron and Muon Source, Science and Technology Facilities Council, \\
Rutherford Appleton Laboratory, Harwell Oxford, Didcot OX11 0QX, UK. \\
${\P}$~Present address: Department of Food Technology, Lund University, SE-211 00 \\
Lund, Sweden. \\
$\ddag$~These authors have contributed equally to the work presented within. \\
$\ast$~k.edler@bath.ac.uk; tom.arnold@esss.se}

@@

The major difference between the two heads is the fact PG head is negatively charged whereas the PC head is zwitterionic (Figure \ref{fig:heads}).
It has been shown previously that, due to the electrostatic interaction, the conformation of the PC head is folded in water\cite{Gilliams2016}.
A similar structure may occur for the PG head, with a weaker interaction between the partially postively-charged alcoholic hydrogen atoms and the negatively-charged phosphate group.
Therefore, the observed increase found for the PG volume in DES when compared with water may be due to the unfolding of the PG head, where the solvent is capable of providing a greater screening effect to the PG head than that present in water.
This may not be observed for the PC head due to the greater strength of the folding interaction arising from the formally-charged nature of the ammonium group.
It would be anticipated that this unfolding would result in an increase in the thickness of the lipid head layer.
Previously, DPPG has been reported to have a head layer thickness of \SI[separate-uncertainty=true]{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} from NR measurements\cite{Clifton2012}, which it slightly less than the \input{../output/dmpg/head.txt}\si{angstrom} determined in the current work, further suggesting that the unfolding of the PG head.
Previously, the presence of short range, electrostatic interactions has been noted to impact the solution structure adopted by zwitterionic surfactants in choline chloride:glycerol\cite{Sanchez-Fernandez2018}.

@@

\bibliography{rsc}% Produces the bibliography via BibTeX.
\bibliographystyle{rsc}
\end{document}

>>>>

\institution{${a}$~Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK. \\
${b}$~Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK. \\
${c}$~European Spallation Source, SE-211 00 Lund, Sweden. \\
${d}$~Department of Physical Chemistry, Lund University, SE-211 00 Lund, Sweden. \\
${e}$~Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble, France. \\
${f}$~Division of Pharmacy and Optometry, University of Manchester, Manchester, \\
M13 9PT, UK. \\
${g}$~ISIS Neutron and Muon Source, Science and Technology Facilities Council, \\
Rutherford Appleton Laboratory, Harwell Oxford, Didcot OX11 0QX, UK. \\
${\P}$~Present address: Department of Food Technology, Lund University, SE-211 00 \\
Lund, Sweden. \\
$\ddag$~These authors have contributed equally to the work presented within. \\
$\ast$~k.edler@bath.ac.uk; tom.arnold@esss.se}

@@

The major difference between the two heads is the fact PG head is negatively charged whereas the PC head is zwitterionic (Figure \ref{fig:heads}).
It has been shown previously that, due to the electrostatic interaction, the conformation of the PC head is folded in water\cite{Gilliams2016}.
A similar structure may occur for the PG head, with a weaker interaction between the partially postively-charged alcoholic hydrogen atoms and the negatively-charged phosphate group.
Therefore, the observed increase found for the PG volume in DES when compared with water may be due to the unfolding of the PG head, where the solvent is capable of providing a greater screening effect to the PG head than that present in water.
This may not be observed for the PC head due to the greater strength of the folding interaction arising from the formally-charged nature of the ammonium group.
It would be anticipated that this unfolding would result in an increase in the thickness of the lipid head layer.
Previously, DPPG has been reported to have a head layer thickness of \SI[separate-uncertainty=true]{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} from NR measurements\cite{Clifton2012}, which it slightly less than the \input{../output/dmpg/head.txt}\si{\angstrom} determined in the current work, further suggesting that the unfolding of the PG head.
Previously, the presence of short range, electrostatic interactions has been noted to impact the solution structure adopted by zwitterionic surfactants in choline chloride:glycerol\cite{Sanchez-Fernandez2018}.

@@

\setlength{\bibsep}{1pt}
\bibliography{rsc}% Produces the bibliography via BibTeX.
\bibliographystyle{rsc}
\end{document}

### 2018-09-10 reports/si.tex
Getting only the preprint on git@
cleaning the SI a bit

\documentclass[11pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[super,sort&compress,comma]{natbib}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[detect-all]{siunitx}
\usepackage{xr}
\externaldocument{apssamp}
\usepackage{rotating}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thetable}{S\Roman{table}}
\author{A.~R.~McCluskey,\textit{$^{ab}$}$^{\ddag}$ A.~Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ \\
K.~J.~Edler,\textit{$^{a}$}$^{\ast}$ S.~C.~Parker,\textit{$^{a}$} A.~J.~Jackson,\textit{$^{cd}$} \\
R.~A.~Campbell,\textit{$^{ef}$} and T.~Arnold\textit{$^{abcg}$}$^{\ast}$ \\
 \\
\textit{$^{a}$~Department of Chemistry, University of Bath, Claverton} \\
\textit{Down, Bath, BA2 7AY, UK.} \\
\textit{$^{b}$~Diamond Light Source, Harwell Campus, Didcot, OX11 0DE,} \\
\textit{UK.} \\
\textit{$^{c}$~European Spallation Source, SE-211 00 Lund, Sweden.} \\
\textit{$^{d}$~Department of Physical Chemistry, Lund University,} \\
\textit{SE-211 00 Lund, Sweden.} \\
\textit{$^{e}$~Institut Laue-Langevin, 71 avenue des Martyrs, 38000,} \\
\textit{Grenoble, France.} \\
\textit{$^{f}$~Division of Pharmacy and Optometry, University of} \\
\textit{Manchester, Manchester, M13 9PT, UK.} \\
\textit{$^{g}$~ISIS Neutron and Muon Source, Science and Technology} \\
\textit{Facilities Council, Rutherford Appleton Laboratory, Harwell} \\
\textit{Oxford, Didcot OX11 0QX, UK.} \\
\textit{$^{\P}$~Present address: Department of Food Technology, Lund} \\
\textit{University, SE-211 00 Lund, Sweden}}
\title{SI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''}
\date{}
\begin{document}

>>>>

\documentclass[11pt,a4paper]{paper}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[super,sort&compress,comma]{natbib}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[detect-all]{siunitx}
\usepackage{xr}
\externaldocument{apssamp}
\usepackage{rotating}
\usepackage[margin=2cm]{geometry}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thetable}{S\Roman{table}}
\title{SI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''}
\author{A.~R.~McCluskey,\textit{$^{ab}$}$^{\ddag}$ A.~Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ K.~J.~Edler,\textit{$^{a}$}$^{\ast}$ \\
S.~C.~Parker,\textit{$^{a}$} A.~J.~Jackson,\textit{$^{cd}$} R.~A.~Campbell,\textit{$^{ef}$} and T.~Arnold \textit{$^{abcg}$}$^{\ast}$}

\institution{${a}$~Department of Chemistry, University of Bath, Claverton Down, Bath, \\
BA2 7AY, UK. \\
${b}$~Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK. \\
${c}$~European Spallation Source, SE-211 00 Lund, Sweden. \\
${d}$~Department of Physical Chemistry, Lund University, SE-211 00 Lund, Sweden. \\
${e}$~Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble, France. \\
${f}$~Division of Pharmacy and Optometry, University of Manchester, Manchester, \\
M13 9PT, UK. \\
${g}$~ISIS Neutron and Muon Source, Science and Technology Facilities Council, \\
Rutherford Appleton Laboratory, Harwell Oxford, Didcot OX11 0QX, UK. \\
${\P}$~Present address: Department of Food Technology, Lund University, SE-211 00 \\
Lund, Sweden. \\
$\ddag$~These authors have contributed equally to the work presented within. \\
$\ast$~k.edler@bath.ac.uk; tom.arnold@esss.se}

\date{\today}

\begin{document}
